Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-26 paper/paper.Rmd
move sptcv_cstf paragraph from discussion to methods section

@@

<!-- sptcv LLO & LTO: requires additional variable to specify groupings -->
The `"spcv_cstf"` methods (with only one of `space_var` or `time_var` set) require a variable in the dataset which should be used for grouping.
The specification of such is not always easy because the grouping should ensure that the selected groups inherit substantial autocorrelation within themselves and simultaneously differ substantially from other groups.
Also, if the selected variable contains too many groups, the difference within train/test splits may become undesirably high and tend towards a LOO CV [@meyer2018].

>>>>

The `"spcv_cstf"` methods LLO and LTO (with only one of `space_var` or `time_var` set) require a variable in the dataset which should be used for grouping.
The specification of the variable(s) which should be used for a spatial, temporal or spatiotemporal grouping is not trivial because the final partitioning should, in the optimal case, ensure that the selected groups inherit substantial autocorrelation within themselves and simultaneously differ substantially from other partitions.
Also, if the selected variable contains too many groups, the difference within train/test splits may become undesirably high and tend towards a LOO CV [@meyer2018].

@@
